---
title: "1_1"
output:
  html_document: default
  pdf_document: default
date: "2023-07-12"
other: " using ames data set: bar,hist,summary func,count,kernel,histdensity,QQplot,boxplots"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r packages}
options(repos = "https://cran.rstudio.com")
install.packages('AmesHousing')
install.packages('tidyverse')
library(AmesHousing)
library(tidyverse)
install.packages("Hmisc")
library(Hmisc)
```
```{r}
install.packages('tinytex')
tinytex::install_tinytex(force = TRUE)
```

## formatted ames dataset

```{r}
ames <- make_ordinal_ames() 
#str(ames)
```
## ggplot bargraphh - nominal
```{r, echo=FALSE}
ggplot(data = ames) +
  geom_bar(mapping = aes(x = Heating_QC), fill = "Orange") + labs(x = "Heating System Quality", y ="Frequency", title ="Bar Graph of Heating System")
```
## count - nominal
```{r}
ames %>%
  count(Heating_QC)
```
## ggplot histogram interval estimate

```{r}
ggplot(data = ames) +
  geom_histogram( mapping = aes(x = Sale_Price/1000), fill = "Blue") + labs(x ="Sales Price (Thousands $)", title ="Histogram of Sales Price in Thousands of Dollars", y ="Frequency")
```

## summary functions in R
```{r first}
summary(ames$Sale_Price)
```


```{r second(Himsc)}

Hmisc::describe(ames$Sale_Price)
```
```{r  third ( tidyverse)}
library(tidyverse)
ames %>% 
  group_by(Exter_Qual) %>%
  dplyr::summarise( average = mean(Sale_Price), st_dev = sd(Sale_Price), maximum = max(Sale_Price), minimum = min(Sale_Price))

```
##histogram & kernal density estimator ( provide x in ggplot function***, ..density.. in y)
```{r, echo = FALSE}
library(ggplot2)
ggplot(data = ames, aes(x=Sale_Price/1000)) + 
  geom_histogram(aes( y=..density..), alpha=0.5) + geom_density( alpha = 0.2) +
    labs(x = "Sales Price (Thousands $)")  

```
## 2 dist of sales one for each central air
```{r}
ggplot(data = ames, aes(x=Sale_Price/1000)) +
  geom_histogram(data = subset(ames, Central_Air == 'Y'), aes(fill = Central_Air), alpha = 0.2) +
  geom_histogram(data = subset(ames, Central_Air == 'N'), aes(fill = Central_Air), alpha = 0.2) +
  labs(x = "Sales Price (Thousands $)")  + scale_fill_manual(name="Central_Air",values=c("red","blue"),labels=c("No","Yes"))
```

## normalize that quantity and compare the raw probability densitites
```{r}
ggplot(ames,aes(x=Sale_Price/1000)) + 
    geom_histogram(data=subset(ames,Central_Air == 'Y'),aes(y=..density..,fill=Central_Air), alpha = 0.2) +
    geom_histogram(data=subset(ames,Central_Air == 'N'),aes(y=..density..,fill=Central_Air), alpha = 0.2) +
    labs(x = "Sales Price (Thousands $)") 
```
## to ease our effort in differentiating histogram, we can use kernel ( better way than histogram with density****)
```{r}

ggplot(ames,aes(x=Sale_Price/1000)) + 
    geom_density(data=subset(ames,Central_Air == 'Y'),aes(fill=Central_Air), alpha = 0.2) +
    geom_density(data=subset(ames,Central_Air == 'N'),aes(fill=Central_Air), alpha = 0.2) +
    labs(x = "Sales Price (Thousands $)")  
```

## normal probability or QQ plots
```{r}
ggplot(data = ames, aes(sample = Sale_Price/1000)) +
  stat_qq() +
  stat_qq_line()
```
##box plot
```{r}
  ggplot(data = ames, aes(y = Sale_Price/1000))+
  geom_boxplot()+
  labs(y = "sales price")
```

##box plot to diff levels of categorical variable
```{r}
ggplot(data = ames, aes(y = Sale_Price/1000,x = Central_Air, fill = Central_Air))+
  geom_boxplot()+
  labs(y = "sales price",x = "Central Air")+
  scale_fill_brewer(palette="Accent") + theme_classic() + coord_flip()
```

